Realistic real-time rendering of skin under consideration of physical basis

### 2020-06-22 presentation.tex
paper: backup of written chapters and notes so far

  \blfootnote{Formula taken from: \cite[p.~352]{real-time-rendering}, which in turn cites \cite{kelemen2001microfacet}}
  \blfootnote{Image taken from: \citet{efficient-human-skin-rendering}}

>>>>

  \footnote{Formula taken from: \cite[p.~352]{real-time-rendering}, which in turn cites \cite{kelemen2001microfacet}}
  \footnote{Image taken from: \citet{efficient-human-skin-rendering}}
